\section{Literature Review}
\subsection{Operation, Subsystems and Parameters}
Every day we rely on a wide range of machines, but every machine eventually breaks down unless it’s being maintained.  

The control, monitoring and maintenance of ship equipment is fundamental to efficient engine room performance . Sensors and actuators play an important role in operation of various machines such as pumps, generators, among others. Therefore, they must always be in proper working condition. To guarantee this, machines are constantly monitored and types of maintenance of their components are performed. Corrective maintenance is performed in the case of a critical failure in the equipment and causes an unplanned downtime of the production line. Scheduled maintenance is performed periodically and equipment is checked and replaced, if necessary, in order to avoid unplanned downtime. Industry has begun to perform condition-based maintenance where predictive equipment status is used to plan a maintenance \cite{noauthor_predictive_nodate}.

Condition monitoring is a type of maintenance inspection where an operational asset is monitored and the data obtained is analysed to detect signs of degradation, diagnose the cause of faults, and predict for how long it can be safely or economically run. There are five general categories of Condition Monitoring techniques—vibration monitoring and analysis; visual inspection and non-destructive testing; performance monitoring and analysis; analysis of wear particles in lubricants and of contaminants in process fluids; and electrical plant testing. Condition monitoring needs a good quality data such as that obtained by carefully run tests. However, much useful information can often be obtained from a plant’s permanent instrumentation once repeatability is established\cite{lu_condition_2018}. The basic principle of condition monitoring is to indicate the occurrence of deterioration by taking physical measurements at regular intervals. Condition-based monitoring is used to inspect and replace the system according to the observed deterioration level. 

Predictive maintenance is referred to as the use of data, machine learning techniques, and statistical algorithms to predict the most likely failure outcome of systems \cite{tinga_predictive_2017}. The machinery data collected by monitors say sensors (wired or wireless), is analysed in order to provide a consistent forecast on when a given component or machinery should be replaced or maintained thus optimizing on maintenance cost and downtime. Predictive maintenance is a branch of condition-based monitoring. Condition based monitoring (CBM) is described as a maintenance practice that tolerates and detects the failure of a system during operation through continuous monitoring of the system during operation\cite{kimera_predictive_2020}. 

Marine vehicle managers and marine technical experts claim that installation of more sensors and cables for monitoring purposes, will only have an impact on maintenance of marine systems only if the maintenance crew apply, hand-in-hand, other maintenance aspects like visual inspections, vibration measurements, regular oil analysis and enriching the maintenance information base with performance parameters \cite{kimera_predictive_2020}. 

Remaining Useful Life (RUL) is the time remaining for a component to perform its functional capabilities before failure. The concept of RUL is used to predict the life-span of components (of a service system) with the purpose of minimizing catastrophic failure events in both manufacturing and service sectors. This project involves acquiring real data from a normal working pump at its different stages in life. This will be done using multiple sensors attached to the pump at different times under different working conditions. Over time, the installed sensors will generate more and more data which can be used to improve the initial models and make near-perfect failure predictions. 

Currently, the industry is majorly relying on sensors for condition monitoring which has facilitated decision making under time constraints. The time between the point where a potential failure occurs and the point where it deteriorates into a functional failure can be seen as an opportunity window during which decision-making algorithms can recommend actions with the aim to eliminate the anticipated functional failure or mitigate its effect. The system can record and monitor pressure and temperature conditions of an industrial motor and transmit the data through a wireless network to a data logging centre. The current prototype was developed using open-source software and hardware and can successfully identify abnormal motor conditions from sensor input values that exceed predefined set-points. 

The widespread use of sensors in industry allows for data acquisition, which, combined with advanced methods of analysis, can significantly improve and optimize production. Therefore, the data can be used not only to monitor the current state of the process and devices, but also to predict this failure state. The application of predictive methods to sensory data representing production process, including machine condition, allows for early identification and prediction of the faulty or hazardous process state or machine break down.

The aim of this project is to present a data-driven method analysing sensory data to predict machine failure or identify its deteriorating condition, so that users can plan maintenance work and avoid unplanned downtime. This method was prepared based on real-life data with the assumption that the created solution will be used in industry as a result of the implemented project. 

Predictive maintenance is based on the prognostic and health management technology, which supposes that the remaining useful life of equipment can be predicted. However, due to uncertainty of prognostics there could be wrong decisions regarding the remaining time to failure. 

Currently, the most promising strategy of maintenance for various technical systems and production lines is the predictive maintenance (PM), which can be applied to any system if there is a deteriorating physical parameter like vibration, pressure, voltage, or current that can be measured\cite{sampaio_prediction_2019}.

 Motors are the backbone of industry; they start degrading due to different reasons such as long period of operation, variations of power supply, or harsh environment; which gradually lead to permanent damage.Thus, the monitoring of their condition is of prime importance for sustaining the operation and maintainig efficiency. Consequently, it becomes crucial to monitor the operation continuously \cite{han_motor_2019}. 

Industry reliability surveys suggest that AC motor failures may be divided into five categories, including (IEEE, 1997): 

\begin{itemize}
	\item bearing: 44\% 
	
	\item stator winding: 26\% 
	
	\item rotor: 3\% 
	
	\item shaft: 5\% 
	
	\item others: 22\%. 
\end{itemize}


Even though the replacement of defective bearings is the cheapest to fix among the causes of failure, it is the most difficult one to detect. Motors that are in continuous use cannot be stopped for analysis. 
\subsection{Sensors}
\subsubsection{Temperature Sensor}
A temperature sensor is a device, typically, a thermocouple or resistance temperature detector, that provides temperature measurement in a readable form through an electrical signal. It measures the degree of hotness or coolness of an object. There are many types of temperature sensors, but, the most common way to categorise them is based upon the mode of connection which includes, contact and non-contact temperature sensors\cite{noauthor_temperature_2019}. 

Contact sensors include thermocouples and thermistors because they are in direct contact with the object they are to measure. Whereas, the non-contact temperature sensors measure the thermal radiation released by the heat source. Such temperature meters are often used in hazardous environments like nuclear power plants or thermal power plants. 

In this project the contact type of temperature sensor was selected due to the nature of data to be collected from the bearings. 
\subsubsection{Thermistor}
A thermistor is a temperature sensitive resistor. They are often used as a temperature sensor. The term thermistor is a contraction of the words "thermal" and "resistor". All resistors have some dependency on temperature, which is described by their temperature coefficient. In most cases, the temperature coefficient is minimized, but in the case of thermistors a high temperature coefficient is achieved. Unlike most other resistors, thermistors usually have negative temperature coefficients (NTC) which means the resistance decreases as the temperature increase. Thermal resistors with a positive temperature coefficient are called PTC thermistors (Positive Temperature Coefficient)\cite{noauthor_learn_nodate}.

The DS18B20 is a small temperature sensor with a built in 12bit ADC. It can be easily connected to an Arduino digital input. The sensor communicates over a one-wire bus and requires little in the way of additional components \cite{noauthor_learn_nodate}.

\subsection{Current Sensor}
A current sensor is a device that detects and converts current to an easily measured output voltage, which is proportional to the current through the measured path.

When a current flows through a wire or in a circuit, voltage drop occurs. Also, a magnetic field is generated surrounding the current carrying conductor. Both of these phenomena are made use of in the design of current sensors. Thus, there are two types of current sensing: direct and indirect. Direct sensing is based on Ohm’s law, while indirect sensing is based on Faraday’s and Ampere’s law.



Direct Sensing involves measuring the voltage drop associated with the current passing through passive electrical components.
Indirect Sensing involves measurement of the magnetic field surrounding a conductor through which current passes.
\subsubsection{Pressure Transducer}
Pressure transducers can come in a number of shapes and sizes, but the majority of transducers have a cylinder-shaped centre which houses the diaphragm and the measurement pressure chamber, a pressure port at one end which is typically a threaded, bolted, barbed fitted, or open, and on the other end a location for signal transmission\cite{noauthor_different_nodate}. 




